\section{Limitations}
Although our results suggest a strong potential of CodeGlass and DiffTrack, there are several limitations in our study.
An evaluation with a larger dataset is necessary to investigate the true performance of DiffTrack.
The current DiffTrack implementation generally takes a couple of seconds to identify code pieces in past pull requests.
Our lab study participants did not mention noticeable delays by the system.
Algorithm optimization and speed performance evaluations are out of our main scope though they are important future work.
%Future work should investigate how to optimize its process.

CodeGlass would not be effective if a project does not regularly use pull requests or developers do not write proper descriptions in commits.
Prior work has investigated a tool to support developers to write commit descriptions~\cite{ChangeScribe}, which can co-exist with CodeGlass.
Because information provided through CodeGlass is useful for code comprehension, our system could also encourage a practice of using pull requests and writing detailed comments from a different perspective. 

DiffTrack does not currently support backtracking at a word- or character-level of granularity.
Such a capability would enable new use scenarios (e.g., looking into the implementation history and reasons for a particular variable).
However, very accurate syntactic understanding would be necessary.
Future work should investigate how AST-based methods~\cite{GumTree, Change_Distilling} could support finer-level code examination.

\section{Conclusion}

We presented CodeGlass, an interface that provides pull requests and their review comments associated with a code piece.
%We also developed a piece-level diff backtrack algorithm, called DiffTrack.
Given a code piece, our DiffTrack algorithm identifies its location in an older version even if changes were made.
It precisely and accurately extracts a series of commits that include changes on the chosen code piece.
CodeGlass then shows a series of pull requests containing these commits for supporting user's comprehension.
Our quantitative evaluation on the DiffTrack algorithm shows high precision and recall results for various types of revisions.
In addition, our user study confirmed that CodeGlass was most useful to obtain development rationale and history about code pieces.
Expert reviews confirmed potential advantages of CodeGlass in professional use.
